KidsAIR: Main analysis

### 2021-11-19 child_health_data_summary.Rmd
Minor analysis updates for main paper revisions

>>>>

```{r}
kids_at_home_log <- read_rds(paste0(file_path, "Output/kids_at_home_log.rds"))

at_home_summary <- kids_at_home_log %>% 
  mutate(treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education"))) %>% 
  filter(!is.na(at_home)) %>% 
  arrange(area, home, child_id_num, sampling_day, sample_time) %>% 
  group_by(area, home, child_id_num) %>% 
  mutate(total_n = n(),
         time_home = sum(at_home, na.rm = TRUE),
         at_home_percent = time_home/total_n*100) %>% 
  ungroup() %>% 
  select(area, home, child_id_num, sampling_day, sample_time, treatment_assigned,
         total_n, time_home, at_home, at_home_percent) %>% 
  filter(!is.na(treatment_assigned)) %>% 
  distinct(area, home, child_id_num, .keep_all = T) %>% 
  #group_by(treatment_assigned) %>% 
  summarize(mean_at_home = mean(at_home_percent, na.rm = TRUE),
            sd_at_home = sd(at_home_percent, na.rm = TRUE),
            min_at_home = min(at_home_percent, na.rm = TRUE),
            p25 = quantile(at_home_percent, probs = 0.25),
            median_at_home = median(at_home_percent, na.rm = TRUE),
            p75 = quantile(at_home_percent, probs = 0.75),
            max_at_home = max(at_home_percent, na.rm = TRUE))
at_home_summary

at_home_n <- kids_at_home_log %>% 
  mutate(treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education"))) %>% 
  filter(!is.na(treatment_assigned)) %>% 
  filter(!is.na(at_home)) %>% 
  distinct(area, home, child_id_num, .keep_all = TRUE) %>% 
  count(treatment_assigned)
at_home_n
```

### 2021-11-19 main_analysis_final.Rmd
Minor analysis updates for main paper revisions

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 7 September 2021"
output: pdf_document
---

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10,
                     control = glmerControl(optimizer = "bobyqa"))
#write_rds(itt_results, paste0(file_path, "Output/itt_results.rds"))

@@

# Run function with selected interaction term
# Use next few lines to help fill in Tables for publication
int_function(analysis_data, "residents_smoke")

@@

# Try child_age, gender, home_floors_2level, home_sqft_2level, residents_smoke
```

@@

@@

@@

```{r}  
# Load results
itt_results <- read_rds(paste0(file_path, "Output/itt_results.rds"))
itt_winter1_results <- read_rds(paste0(file_path, "Output/itt_winter1_results.rds"))
itt_noak_results <- read_rds(paste0(file_path, "Output/itt_noak_results.rds"))
#itt_winter2_results <- read_rds(paste0(file_path, "Output/itt_winter2_results.rds"))
itt_income_results <- read_rds(paste0(file_path, "Output/itt_income_results.rds"))
#itt_filter_type_results <- read_rds(paste0(file_path, "Output/itt_filter_type_results.rds"))
#itt_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_filter_comp_results.rds"))
itt_smoke_results <- read_rds(paste0(file_path, "Output/itt_smoke_results.rds"))
itt_burn_level_results <- read_rds(paste0(file_path, "Output/itt_burn_level_results.rds"))
itt_smoking_results <- read_rds(paste0(file_path, "Output/itt_smoking_results.rds"))
itt_windows_results <- read_rds(paste0(file_path, "Output/itt_windows_results.rds"))
itt_door_results <- read_rds(paste0(file_path, "Output/itt_door_results.rds"))
itt_sweep_results <- read_rds(paste0(file_path, "Output/itt_sweep_results.rds"))
itt_ambpm_results <- read_rds(paste0(file_path, "Output/itt_ambpm_results.rds"))
itt_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_ambtemp_results.rds"))
#itt_home_results <- read_rds(paste0(file_path, "Output/itt_home_results.rds"))
itt_outlier_results <- read_rds(paste0(file_path, "Output/itt_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_winter1_tidy <- results_function(itt_winter1_results, "ITT Winter 1")
itt_noak_tidy <- results_function(itt_noak_results, "ITT no AK")
#itt_winter2_tidy <- results_function(itt_winter2_results, "ITT Winter 2")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
#itt_filter_type_tidy <- results_function(itt_filter_type_results, "ITT + filt type")
#itt_filter_comp_tidy <- results_function(itt_filter_comp_results, "ITT + filt comp")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_ambpm_tidy <- results_function(itt_ambpm_results, "ITT + amb PM")
itt_ambtemp_tidy <- results_function(itt_ambtemp_results, "ITT + amb temp")
#itt_home_tidy <- results_function(itt_home_results, "ITT - home")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, itt_noak_tidy,
                              itt_income_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_ambpm_tidy, itt_ambtemp_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", "ITT no AK",
                                   "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  theme_bw() +  
  geom_hline(yintercept =  1) +
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Odds of LRTI compared to Control") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

ITT Primary = Logistic regression mixed model, as specified above  
ITT Winter 1 = Primary model with Winter 1 data only  
ITT no AK = Primary model without homes from AK (different placebo group)  
ITT + income = Primary model plus categorical income variable  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period  
ITT outlier = Primary model with data that fixes incidence outlier

@@

er_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + 
                          amb_temp_lrti + amb_pm_lrti + residents_smoke +
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

@@

lrti_summary_table <- analysis_data_winter1 %>% 
  filter(!is.na(lrti_events_di_winter) & !is.na(pm_mean_sampling_period) &
           !is.na(child_age) & !is.na(education_3level) & !is.na(residents_smoke)) %>% 
  #group_by(treatment_assigned) %>% 
  mutate(lrti_events_num = as.numeric(lrti_events_di_winter),
         lrti_events_num = lrti_events_num - 1) %>%  
  summarize("Total LRTI" = sum(lrti_events_num, na.rm = TRUE),
            "Group %" = `Total LRTI`/n()*100)
lrti_summary_table

lrti_summary_table <- analysis_data_winter1 %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  mutate(lrti_events_num = as.numeric(lrti_events_di_winter),
         lrti_events_num = lrti_events_num - 1) %>% 
  group_by(treatment_filter_type) %>% 
  summarize("Total LRTI" = sum(lrti_events_num, na.rm = TRUE),
            "Group %" = `Total LRTI`/n()*100)
lrti_summary_table
```

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 19 Oct 2021"
output: pdf_document
---

@@

```{r, echo=TRUE}
# Run primary model and print results
itt_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk +
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10,
                     control = glmerControl(optimizer = "bobyqa"))

#write_rds(itt_results, paste0(file_path, "Output/itt_results.rds"))

@@

# Run function with selected interaction term
# Use next few lines to help fill in Tables for publication
int_function(analysis_data, "flu_shot")

@@

# Try child_age, gender, home_floors_2level, home_sqft_2level, residents_smoke, flu_shot
```

@@

itt_fluvax_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + person_time_at_risk + flu_shot + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_fluvax_results, paste0(file_path, "Output/itt_fluvax_results.rds"))

@@

itt_area_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + area + person_time_at_risk + 
                     (1 | home:cohort),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_area_results, paste0(file_path, "Output/itt_area_results.rds"))

itt_offset_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                     child_age + 
                     (1 | home:cohort:area),
                     data = analysis_data, family = binomial, nAGQ = 10)
write_rds(itt_offset_results, paste0(file_path, "Output/itt_offset_results.rds"))

@@

```{r}  
# Load results
itt_results <- read_rds(paste0(file_path, "Output/itt_results.rds"))
itt_winter1_results <- read_rds(paste0(file_path, "Output/itt_winter1_results.rds"))
itt_noak_results <- read_rds(paste0(file_path, "Output/itt_noak_results.rds"))
#itt_winter2_results <- read_rds(paste0(file_path, "Output/itt_winter2_results.rds"))
itt_income_results <- read_rds(paste0(file_path, "Output/itt_income_results.rds"))
#itt_filter_type_results <- read_rds(paste0(file_path, "Output/itt_filter_type_results.rds"))
#itt_filter_comp_results <- read_rds(paste0(file_path, "Output/itt_filter_comp_results.rds"))
itt_smoke_results <- read_rds(paste0(file_path, "Output/itt_smoke_results.rds"))
itt_burn_level_results <- read_rds(paste0(file_path, "Output/itt_burn_level_results.rds"))
itt_smoking_results <- read_rds(paste0(file_path, "Output/itt_smoking_results.rds"))
itt_windows_results <- read_rds(paste0(file_path, "Output/itt_windows_results.rds"))
itt_door_results <- read_rds(paste0(file_path, "Output/itt_door_results.rds"))
itt_sweep_results <- read_rds(paste0(file_path, "Output/itt_sweep_results.rds"))
itt_ambpm_results <- read_rds(paste0(file_path, "Output/itt_ambpm_results.rds"))
itt_ambtemp_results <- read_rds(paste0(file_path, "Output/itt_ambtemp_results.rds"))
itt_fluvax_results <- read_rds(paste0(file_path, "Output/itt_fluvax_results.rds"))
itt_home_results <- read_rds(paste0(file_path, "Output/itt_home_results.rds"))
itt_area_results <- read_rds(paste0(file_path, "Output/itt_area_results.rds"))
itt_offset_results <- read_rds(paste0(file_path, "Output/itt_offset_results.rds"))
itt_outlier_results <- read_rds(paste0(file_path, "Output/itt_outlier_results.rds"))

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_winter1_tidy <- results_function(itt_winter1_results, "ITT Winter 1")
itt_noak_tidy <- results_function(itt_noak_results, "ITT no AK")
#itt_winter2_tidy <- results_function(itt_winter2_results, "ITT Winter 2")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
#itt_filter_type_tidy <- results_function(itt_filter_type_results, "ITT + filt type")
#itt_filter_comp_tidy <- results_function(itt_filter_comp_results, "ITT + filt comp")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_ambpm_tidy <- results_function(itt_ambpm_results, "ITT + amb PM")
itt_ambtemp_tidy <- results_function(itt_ambtemp_results, "ITT + amb temp")
itt_fluvax_tidy <- results_function(itt_fluvax_results, "ITT + flu vax")
itt_home_tidy <- results_function(itt_home_results, "ITT no Home")
itt_area_tidy <- results_function(itt_area_results, "ITT area fixed")
itt_offset_tidy <- results_function(itt_offset_results, "ITT no offset")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

# Combine cleaned results
itt_results_combined <- rbind(itt_tidy, itt_winter1_tidy, itt_noak_tidy,
                              itt_income_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_ambpm_tidy, itt_ambtemp_tidy, itt_fluvax_tidy, 
                              itt_area_tidy, itt_offset_tidy, itt_home_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT Winter 1", "ITT no AK",
                                   "ITT + income", 
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT + amb PM", "ITT + amb temp", "ITT + flu vax", 
                                   "ITT area fixed", "ITT no offset", "ITT no Home"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  theme_bw() +  
  geom_hline(yintercept =  1) +
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Odds of LRTI compared to Control") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

@@

ITT Primary = Logistic regression mixed model, as specified in main results  
ITT Winter 1 = Primary model with Winter 1 data only  
ITT no AK = Primary model without homes from Alaska (different placebo group)  
ITT + income = Primary model plus categorical income variable  
ITT + smoke hx = Primary model plus self-reported smoking variable  
ITT + burn level = Primary model plus self-reported burn-level compared to typical  
ITT + smoke act = Primary model plus # days during sampling with smoking  
ITT + window act = Primary model plus # days during sampling with windows open  
ITT + door act = Primary model plus # days during sampling with doors open  
ITT + sweep act = Primary model plus # days during sampling with sweeping/cleaning  
ITT + amb PM = Primary model plus amb PM during LRTI at-risk period  
ITT + amb temp = Primary model plus amb temp during LRTI at-risk period  
ITT + flu vax = Primary model plus caregiver-reported influenza vaccination status of child  
ITT area fixed = Primary model with area as a fixed term instead of a random term
ITT no offset = Primary model without fixed offset term for person-time of follow-up
ITT no Home = Primary model without the random nested term for household/home

@@

er_results <- glmer(lrti_events_di_total ~ pm_mean_sampling_period_iqr + 
                          child_age + gender + 
                          race_parent + gender_parent +
                          income_3level + education_3level + 
                          amb_temp_lrti + 
                          #amb_pm_lrti + 
                          residents_smoke +
                          person_time_at_risk +
                          (1 | home:cohort:area), 
                          data = analysis_data, family = binomial, nAGQ = 10,
                          control = glmerControl(optimizer = "bobyqa"))
#write_rds(er_results, paste0(file_path, "Output/er_results.rds"))

@@

lrti_summary_table <- analysis_data_winter2 %>% 
  #filter(!is.na(lrti_events_di_winter) & !is.na(pm_mean_sampling_period) &
   #        !is.na(child_age) & !is.na(education_3level) & !is.na(residents_smoke)) %>% 
  #group_by(treatment_assigned) %>% 
  mutate(lrti_events_num = as.numeric(lrti_events_di_winter),
         lrti_events_num = lrti_events_num - 1) %>%  
  filter(area == "AK") %>% 
  group_by(treatment_assigned) %>% 
  summarize("Total LRTI" = sum(lrti_events_num, na.rm = TRUE),
            "Group %" = `Total LRTI`/n()*100,
            n())
lrti_summary_table

lrti_summary_table <- analysis_data_winter1 %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  mutate(lrti_events_num = as.numeric(lrti_events_di_winter),
         lrti_events_num = lrti_events_num - 1) %>% 
  group_by(treatment_filter_type) %>% 
  summarize("Total LRTI" = sum(lrti_events_num, na.rm = TRUE),
            "Group %" = `Total LRTI`/n()*100)
lrti_summary_table

person_time_summary <- analysis_data %>% 
  group_by(treatment_assigned) %>% 
  summarize(mean_var = mean(person_time_at_risk), 
            sd_var = sd(person_time_at_risk), 
            n_var = n(), 
            min_var = min(person_time_at_risk), 
            p25 = quantile(person_time_at_risk, probs = 0.25),
            med_var = median(person_time_at_risk), 
            p75 = quantile(person_time_at_risk, probs = 0.75), 
            max_var = max(person_time_at_risk))
person_time_summary
```
